Analytic reproducibility in articles receiving open data badges at Psychological Science: An observational assessment

### 2020-07-08 manuscript/manuscript.Rmd
adjustment to display plot in manuscript
adjusted keywords

keywords          : "open data, badges, reproducibility, open science, meta-research, journal policy"

@@

```{r}
source(here('analysis','meta_analysis.R'))
```

```{r fig.cap="Forest plot showing the proportion of articles with fully reproducible target outcomes in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.path="figs/"}
include_graphics(here('manuscript', 'figs', 'forestPlot.png'))
```

>>>>

keywords          : "open data, open badges, reproducibility, open science, meta-research, journal policy, research transparency"

@@

```{r fig.cap="Forest plot showing the proportion of articles with fully reproducible target outcomes in Hardwicke et al. (2018) and the present study before and after contacting original authors for assistance with reproducibility checks. Squares represent individual study proportions (with size proportional to meta-analytic weighting). Diamonds represent summary proportions estimated by random effects (RE) models. Error bars represent 95% confidence intervals (CIs).", fig.width=8, fig.path="figs/"}
source(here('analysis','meta_analysis.R'))
```
